### 2022-11-15 NSF2022/Description/broaderimpacts.tex
touch up

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences,
the proposal supports two undergraduate researchers
(URs) per year at Fordham University---for eight summer weeks.
The UR will collaborate directly with PI Ryham,
receive tutorials e.g., numerical methods,
and be guided on mathematical writing and presentation.
Fordham Mathematics recently completed a collaboration studio 
purpose-built for UR support.
Work products include a summary manuscript,
a presentation in the Fordham Undergraduate Research Symposium
and departmental seminars, and participation in a national conference.
We have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep,topsep=0pt]
\item Translate project code from MATLAB into a compiled language 
\item Use machine learning to post-process data of granule dynamics
\item Investigate geometrical self-assembly and generate visualizations
\end{enumerate}
PI Ryham has worked side-by-side with dozens of
undergraduates and high-schoolers in
supported summer research, Girls in Science Technology and Mathematics,
and the Clare Boothe Luce Scholarship program
and the activity benefited their careers in
machine learning, water resources engineering, threat detection,
and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on election redistricting.
The PI is finishing works on the energy density lipid  bilayers
with a recently graduated UR, now working at Raytheon Technologies.
His published works~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16} include
four undegraduate coauthors.

To increase the participation of women,
persons with disabilities and underrepresented minorities in STEM,
the PIs will specifically target students
whose socio-economic background prevents them from participating in
out-of-state research experiences.
The inclusion objective will be aided by the fact that  
Fordham's class of 2026 weighs in with 63 \% women
and more than 46 \% domestic students of color. 
PI Ryham will solicit applicants from
Fordham University's Collegiate Science and Technology Entry Program.
Students from the Bronx High School of Science (PI Ryham) and Newark
Science Park High School (PI Young) will also be encouraged to join the
research team.

>>>>

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences,
the proposal supports two undergraduate researchers
(URs) per year at Fordham University---for eight summer weeks.
The URs will collaborate directly with the PIs,
receive tutorials e.g., numerical methods,
and be guided on mathematical writing and presentation.
Fordham Mathematics recently completed a collaboration studio 
purpose-built for UR support.
Work products include a summary manuscript,
a presentation in the Fordham Undergraduate Research Symposium
and departmental seminars, and participation in a national conference.
We have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep,topsep=0pt]
\item Translate project code from MATLAB into a compiled language 
\item Use machine learning to post-process data of granule dynamics
\item Investigate geometrical self-assembly and generate visualizations
\end{enumerate}
PI Ryham has worked side-by-side with dozens of
undergraduates and high-schoolers in
supported summer research, Girls in Science Technology and Mathematics,
and the Clare Boothe Luce Scholarship program
and the activity benefited their careers in
machine learning, water resources engineering, threat detection,
and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on
polling accessibility in New York City.
The PI is finishing works on energy densities for lipid  bilayers
with a recently graduated UR, now working at Raytheon Technologies.
His publications include works
with seven undegraduate coauthors
~\cite{Figueroa2012CuttingCI, RYHAM20112929, RyWaCo13, RyKlYaCo16}.

To increase the participation of women,
persons with disabilities and underrepresented minorities in STEM,
the PIs will specifically target students
whose socio-economic background prevents them from participating in
out-of-state research experiences.
The inclusion objectives will be aided by the fact that  
Fordham's class of 2026 weighs in with 63 \% women
and more than 46 \% domestic students of color. 
PI Ryham will solicit applicants from
Fordham University's Collegiate Science and Technology Entry Program.
Students from the Bronx High School of Science (PI Ryham) and Newark
Science Park High School (PI Young) will also be encouraged to join the
research team.
